### 2014-06-08 latex/paper2.tex
i think i'm done

Dirac's style and approach to his work has had an enormous influence
on theoretical physics. To fully understand Dirac's style of thinking,
we must begin by looking at Dirac's education and the events that
influenced him.

@@

>>>>

At the turn of the 20th century, many physicists shifted their focus to
investigating the structure of matter and light, being inspired by the
discovery of radioactivity and the electron. Around twenty years later,
their investigations had led them to a new quantum mechanics to describe
the behavior of the atom.  Paul Dirac was one of the most creative
geniuses in theoretical physics during the quantum revolution. Dirac's
style and approach to his work has had an enormous influence on
theoretical physics. In this essay, we explore Dirac's style of physics
by following him through his many accomplishments, but to fully
understand Dirac's style of thinking, we must begin by looking at
Dirac's education and the events that influenced him.

@@

Dirac had a large influence on the physicists Schwinger and Feynman.
Both had read Dirac's book \textit{The Principles of Quantum Mechanics}
during their studies, and were inspired to develop a consistent quantum
electrodynamics, which they accomplished through renormalization.
However, Dirac, always looking for mathematical beauty in physical laws,
felt the renormalization approach was ugly. He never accepted Schwinger
and Feynman's quantum electrodynamics as a satisfactory theory, despite
its successes at predicting experimental results. Dirac was never
successful developing a quantum electrodynamics that satisfied himself
either. In the last paragraph of his book, he writes, ``It would seem
that we have followed as far as possible the path of logical development
of the ideas of quantum mechanics as they are at present understood. The
difficulties, being of a profound character, can be removed only by some
drastic change in the foundations of the theory, probably a change as
drastic as the passage from Bohr's orbit theory to the present quantum
mechanics'' \cite[pg. 310]{principles}.

Dirac's style of thinking has left a significant mark in theoretical
physics. He showed the power of mathematical reasoning in discovering
new laws of nature, although his way of doing mathematics was heavily
influenced by his engineering background. Through guessing equations,
playing with mathematical objects, and seeking beautiful relationships
among these objects, Dirac made some of the greatest advances in physics
following the formulation of quantum mechanics by Heisenberg and
Schrodinger. His style and methods have continued to help physicists
create new laws and predict the existence of new particles, and we see
his influence on physics everywhere even today.
